---
title: "Assignment 5"
author: "Ben Wolin"
date: "2024-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intoduction
The purpose of this assignment is to load in a given csv and perform analysis to compare 2 airlines. These comaperisons will be based on the arrival delays for both airlines. When complete an R Markdown file will be posted to Github and Rpubs.

## Loading Libraries
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
```

## Loading in data from the CSV
```{r}
Flights = read.csv('https://raw.githubusercontent.com/bwolin99/TestRepo/refs/heads/main/Assignment%205/Assignment5_Flights.csv');
```

## Transforming data to prepare it for analysis
```{r}
names(Flights)[1:2] <- c('Airline','Delay')
Flights = Flights[-3, ]
Flights[2,1] = 'Alaska'
Flights[4,1] = 'AM West'
Flights = gather(Flights,'Destination','Count',3:7)
Flights = spread(Flights,key = Delay,value = Count)
names(Flights)[4] = 'on_time'
head(Flights)
```

## Analyzing the Data
```{r}
Flights = Flights %>%
  mutate(Delay_Rate = delayed/(on_time + delayed))

Flights = Flights %>%
  mutate(On_Time_Rate = 1 - Delay_Rate)
head(Flights)
```
Now we will calculate the mean and median delay rates for each airline.
```{r}
Alaska = Flights[Flights$Airline == 'Alaska',]
AM_West = Flights[Flights$Airline == 'AM West',]
Airlines = c('AM West','Alaska')
Mean_DRate = c(mean(AM_West$Delay_Rate),mean(Alaska$Delay_Rate))
Mean_ORate = c(mean(AM_West$On_Time_Rate),mean(Alaska$On_Time_Rate))
Median_DRate = c(median(AM_West$Delay_Rate),median(Alaska$Delay_Rate))
Median_ORate = c(median(AM_West$On_Time_Rate),median(Alaska$On_Time_Rate))
Results = data.frame(Airlines,Mean_DRate,Mean_ORate,Median_DRate,Median_ORate)
head(Results)
```

Looking at these results we can see that AM West has a lower On Time Rate and a higher Delay Rate. This observation can be seen in both median and mean of the rates for all destinations. In conclusion, Alaska is on time more often and is therefore a better Airline in that regard.