---
title: "Assignment 7"
author: "Ben Wolin"
date: "2024-10-13"
output: html_document
---
## Introduction
The purpose of this assignment it to familiarize ourselves with different formats of stored data. I have created 3 identical tables in 3 different file types (XML, HTML, and JSON). We will now be loading these files into our R environment.

## XML
Here we load in our XML file and take a look at the structure.
```{r}
library(xml2)
library(XML)
library(dplyr)
books_XML <- read_xml(url("https://raw.githubusercontent.com/bwolin99/TestRepo/refs/heads/main/Assignment%207/Books.XML"))
xml_structure(books_XML)
```
Next we extract the columns and put them into an R dataframe.
```{r}
Names <- books_XML %>%
  xml_find_all("//Title") %>%
  xml_text()
Author1 <- books_XML %>%
  xml_find_all("//Author1") %>%
  xml_text()
Author2 <- books_XML %>%
  xml_find_all("//Author2") %>%
  xml_text()
Genre <- books_XML %>%
  xml_find_all("//Genre") %>%
  xml_text()

books_xml_final <- data.frame("Title" = Names, "Author 1" = Author1, "Author 2" = Author2, "Genre" = Genre) 

books_xml_final
```

## HTML
Here we load in our HTML table and tidy it to be a neet dataframe.
```{r}
library(rvest)
books_html <- read_html(url("https://raw.githubusercontent.com/bwolin99/TestRepo/refs/heads/main/Assignment%207/Books.html"))

books_html_final <- books_html %>%
  html_element("body") %>%
  html_table()

books_html_final
```

## JSON
With the jsonlite library, we don't even need to tidy our JSON file, the fromJson function will do this for us.
```{r}
library(jsonlite)
books_json <- fromJSON(url("https://raw.githubusercontent.com/bwolin99/TestRepo/refs/heads/main/Assignment%207/Books.json"))

books_json
```

