---
title: DATA 606 Data Project Proposal
author: Ben Wolin
---

### Data Preparation
This data comes from the world bank data catalog, and is a combination of data from these two different datasets.
https://energydata.info/dataset/world-climate-watch/resource/47608ee8-92b9-4611-ba6f-720662193e25
https://energydata.info/dataset/world-climate-watch/resource/1631a4e8-a59a-4026-aa36-162df9b15340

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
library(tidyr)
Emissions_raw <- read.csv('https://raw.githubusercontent.com/bwolin99/TestRepo/refs/heads/main/606%20Final/Emissions.csv',row.names = NULL)
Emissions <- gather(Emissions_raw, key = 'year', value = 'Aggricultural Emissions',3:31)
head(Emissions)
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Does the amount of meat eaten in a country on a given year correlate with the amount of agricultural CO2 that is released in that year. 


### Cases 

**What are the cases, and how many are there?**

Each case represents a specific year in a specific country 


### Data collection 

**Describe the method of data collection.**



### Type of study 

**What type of study is this (observational/experiment)?**



### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**




### Describe your variables?

**Are they quantitative or qualitative**

**If you are are running a regression or similar model, which one is your dependent variable?**


### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r}

```
